Breadth First Searches Over Evolving Graphs

### 2016-01-23 paper.tex
Rewrite abstract

\begin{abstract}
We present a generalization of the breadth first search (BFS) algorithm on
evolving graphs and prove its correctness. The BFS generates paths with nontrivial
structure, which we term temporal paths. We also show with simple counterexamples
that simple products of adjacency matrices do not have the correct combinatorial
properties of enumerating temporal paths. On the contrary, the correct generalization
of BFS requires careful tracking of active nodes which participate in the definition
of edges at specific times. We discuss how the structure of temporal paths leads
to nontrivial matrix structure in adjacency matrix representations of evolving
graphs, as well as implications for real world applications
such as the analysis of citation networks.
\end{abstract}

>>>>

\begin{abstract}
We generalize the breadth first search (BFS) algorithm to evolving graphs and
prove its correctness.
The BFS generates paths with nontrivial structure, which we term temporal paths.
We also show with simple counterexamples that products of adjacency matrices alone
do not have the correct combinatorics of enumerating temporal paths.
Generalizing BFS to evolving graphs requires careful tracking of active nodes
which participate in the definition of edges at specific times.
We discuss how the structure of temporal paths is reflected in adjacency matrix
representations of evolving graphs,
as well as implications for real world applications such as the analysis of citation networks.
\end{abstract}
